---
title: "DV Project Map"
output: html_notebook
---

```{r}
library(readxl)
library(tidyverse)
library (dplyr)
library(ggplot2)
setwd("/Users/Jimballoon/Desktop/YT/")
data <- read.csv(file = 'mental-heath-in-tech-2016_20161114.csv',fileEncoding = "Latin1", check.names = F )
df <- data %>% 
  dplyr::select('Do you currently have a mental health disorder?','Have you ever sought treatment for a mental health issue from a mental health professional?', 'What US state or territory do you work in?','Do you have medical coverage (private insurance or state-provided) which includes treatment of  mental health issues?','Does your employer provide mental health benefits as part of healthcare coverage?')
names(df) <- c('disorder1','treatment','state','mental_insurance','employer_benefit1')
df <- df %>%
  mutate(disorder = case_when(
  disorder1 == 'Yes'  ~ 1,
  disorder1 == 'Maybe'  ~ 0.5,
  disorder1 == 'No'  ~ 0))
df <- df %>%
  mutate(employer_benefit = case_when(
  employer_benefit1 == 'Yes'  ~ 1,
  TRUE  ~ 0))
df <- df %>% 
  dplyr::select('state','treatment','employer_benefit','disorder')
head(df)
```
```{r}
df1 <- df %>% 
  dplyr::select('state','treatment')
df_treatment1 <- df1 %>% group_by(state) %>% summarise(count=n())
df_treatment2 <- df1 %>% filter(treatment==1) %>% group_by(state) %>% summarise(count1=n())
df_treatment <- df_treatment1 %>% 
  left_join(df_treatment2, by = "state") %>% 
  mutate(treatment_prec = count1/count) %>% 
  filter(count>4)

#df_treatment <- df1 %>% group_by(state) %>% summarise(treatment_perc = sum('treatment'== 1))
#df1 <- group_by(df, state) %>% mutate(disorder_percent = disorder/sum(disorder))
#head(df_treatment1)
#sum(df_treatment1$count)
```

```{r}
df2 <- df %>% 
  dplyr::select('state','employer_benefit')
df_employer_benefit1 <- df2 %>% group_by(state) %>% summarise(count=n())
df_employer_benefit2 <- df2 %>% filter(employer_benefit==1) %>% group_by(state) %>% summarise(count1=n())
df_employer_benefit <- df_employer_benefit1 %>% 
  left_join(df_employer_benefit2, by = "state") %>% 
  mutate(employer_benefit_prec = count1/count) %>% 
  filter(count>4)
```

```{r}
df_final <- merge(x = df_employer_benefit, y = df_treatment, by = "state", all = TRUE)  %>%
  dplyr::select('state','treatment_prec','employer_benefit_prec')
df_final$treatment_prec <- scales::percent(df_final$treatment_prec)
df_final$employer_benefit_prec <- scales::percent(df_final$employer_benefit_prec)
#df_final$treatment_prec <- round(df_final$treatment_prec, digits = 2)
#df_final$employer_benefit_prec <- round(df_final$employer_benefit_prec, digits = 2)
```

```{r}
library(rgdal)
library(sp)
library(raster)
library(leaflet)
library(maps)
library(ggmap)
# From https://www.census.gov/geo/maps-data/data/cbf/cbf_state.html
states <- shapefile("/Users/Jimballoon/Downloads/cb_2018_us_state_20m/cb_2018_us_state_20m.shp")

combined <- states@data %>% 
  left_join(df_final, by = c(NAME = "state"))
states@data <- combined

```

```{r}
bins <- c(0, 0.2, 0.4, 0.6, 0.8, 1)
pal <- colorBin("YlOrRd", domain = states$treatment_prec, bins = bins)
labels_states <- paste( states$NAME,
                    "Employee Sougnt Treatment Frequency:", states$treatment_prec)

m <- leaflet() %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>% 
  addPolygons(data=states,
    fillColor = ~pal(treatment_prec),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_states,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(data=states, pal = pal, title = "Frequency of Employee Who Sought Treatment", values = ~treatment_prec, opacity = 0.7,
    position = "bottomright")


m

```

Frequency of employee who sought mental health treatment: Iowa, North Carolina, New Jersey and Connecticut have the highest scores. States with too small sample size are removed (n<5).

```{r}
bins <- c(0, 0.2, 0.4, 0.6, 0.8, 1)
pal <- colorBin("YlOrRd", domain = states$employer_benefit_prec, bins = bins)
labels_states <- paste( states$NAME,
                    "Employer with Mental Healthcare Benefit Frequency:", states$employer_benefit_prec)

n <- leaflet() %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN'))) %>% 
  addPolygons(data=states,
    fillColor = ~pal(employer_benefit_prec),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels_states,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
  addLegend(data=states, pal = pal, title = "Frequency of Employer with Mental Healthcare Benefit", values = ~employer_benefit_prec, opacity = 0.7,
    position = "bottomright")


n
```

Frequency of employer with mental healthcare benefit: Iowa is among the highest, while New Jersey is among the lowest.











